Molecular transport in human pial perivasculature

### 2024-03-12 paper/main.tex
More references

\begin{itemize}
\item Vinje et al~\cite{vinje2021brain} and references therein illustrates the location and characteristics of human pial perivascular spaces.
\item Mestre et al~\cite{mestre2022periarteriolar} study the properties of pial perivascular spaces in detail in mice.
\item Mestre et al~\cite{mestre2018flow} measure and characterize pial perivascular transport and estimate flow magnitudes (in mice).
\item
  Weller and coauthors conducted pioneering studies of perivascular spaces, flow and transport~\cite{zhang1990interrelationships, zhang1992directional}. They identified thin sheaths of pial cells surrounding arteries and arterioles (but not veins or venules) on the brain surface and within the human brain itself~\cite{zhang1990interrelationships}. Further, they observed that tracers spread along perivascular (arterial, venous and capillar) spaces in (rat) grey matter, and in the subarachnoid space (to the cribriform plate and nasal lymphatics)..   
\item In a series of papers, Bakker and coauthors study perivascular anatomy and solute transport~\cite{bedussi2017paravascular, bedussi2018paravascular}. They find that the subarachnoid space, the cisterns, ventricles and penetrating periarteriolar spaces form a continuous cerebrospinal-fluid filled space surrounding and penetrating the rat brain\cite{bedussi2017paravascular}. Moreover, they demonstrate pulsatile and directional (antegrade) flow in perivascular (predominantly periarterial) spaces on the brain surface.
\item Bollman et al~\cite{bollmann2022imaging} image the human pial vasculature at high resolution (7T).
\item Hornkjøl et al~\cite{hornkjol2022csf} model CSF flow and solute transport in the human SAS and brain parenchyma. 
\item Mardal et al~\cite{mardal2022mathematical} give a succinct introduction to MRI-based computational brain modelling. 
\end{itemize}

>>>>

\begin{itemize}
\item Vinje et al~\cite{vinje2021brain} and references therein illustrates the location and characteristics of human pial perivascular spaces.
\item Mestre et al~\cite{mestre2022periarteriolar} study the properties of pial perivascular spaces in detail in mice.
\item Mestre et al~\cite{mestre2018flow} measure and characterize pial perivascular transport and estimate flow magnitudes (in mice).
\item
  Weller and coauthors conducted pioneering studies of perivascular spaces, flow and transport~\cite{zhang1990interrelationships, zhang1992directional}. They identified thin sheaths of pial cells surrounding arteries and arterioles (but not veins or venules) on the brain surface and within the human brain itself~\cite{zhang1990interrelationships}. Further, they observed that tracers spread along perivascular (arterial, venous and capillar) spaces in (rat) grey matter, and in the subarachnoid space (to the cribriform plate and nasal lymphatics)..   
\item In a series of papers, Bakker and coauthors study perivascular anatomy and solute transport~\cite{bedussi2017paravascular, bedussi2018paravascular}. They find that the subarachnoid space, the cisterns, ventricles and penetrating periarteriolar spaces form a continuous cerebrospinal-fluid filled space surrounding and penetrating the rat brain\cite{bedussi2017paravascular}. Moreover, they demonstrate pulsatile and directional (antegrade) flow in perivascular (predominantly periarterial) spaces on the brain surface.
\item
  The architecture of pial and subarachnoid perivascular spaces in the rat brain was also studied by Thorne and colleagues~\cite{pizzo2018intrathecal, hannocks2018molecular}.
\item Bollman et al~\cite{bollmann2022imaging} image the human pial vasculature at high resolution (7T).
\item Hornkjøl et al~\cite{hornkjol2022csf} model CSF flow and solute transport in the human SAS and brain parenchyma. 
\item Mardal et al~\cite{mardal2022mathematical} give a succinct introduction to MRI-based computational brain modelling. 
\item
  Rey et al~\cite{rey2023perivascular} (from the group of Sartinoranont) model and study perivascular transport in rat brain networks.
\end{itemize}
